Weather Data Integration and Assimilation System\\

### 2020-02-10 method/sec_1-architectural_decisions.tex
fix akka ref issues

In the second phase of \acrshort{wdias}, the proposed architecture changed to use with Actor model using AKKA framework \cite{HewittWhyDocumentation} after consider into the disadvantage of using \acrshort{esb}. Using the Actors we tried to implement the microservice architecture. In that case, an Actor or An Actor with slave Actors map into each microservice in the \acrshort{wdias}.

>>>>

In the second phase of \acrshort{wdias}, the proposed architecture changed to use with Actor model using AKKA framework \cite{HewittWhyModel} after consider into the disadvantage of using \acrshort{esb}. Using the Actors we tried to implement the microservice architecture. In that case, an Actor or An Actor with slave Actors map into each microservice in the \acrshort{wdias}.
